% Acknowledgements

\pdfbookmark[1]{Acknowledgements}{Acknowledgements} % Bookmark name visible in a PDF viewer

% \begin{flushright}{\slshape    
% We have seen that computer programming is an art, \\ 
% because it applies accumulated knowledge to the world, \\ 
% because it requires skill and ingenuity, and especially \\
% because it produces objects of beauty.} \\ \medskip
% --- \defcitealias{knuth:1974}{Donald E. Knuth}\citetalias{knuth:1974} \citep{knuth:1974}
% \end{flushright}

\bigskip

%----------------------------------------------------------------------------------------

\begingroup

\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax

\chapter*{Acknowledgements}

% \noindent Put your acknowledgements here.\\
% 
% \noindent Many thanks to everybody who already sent me a postcard!\\
% 
% \noindent Regarding the typography and other help, many thanks go to Marco Kuhlmann, Philipp Lehman, Lothar Schlesier, Jim Young, Lorenzo Pantieri and Enrico Gregorio\footnote{Members of GuIT (Gruppo Italiano Utilizzatori di \TeX\ e \LaTeX )}, J\"org Sommer, Joachim K\"ostler, Daniel Gottschlag, Denis Aydin, Paride Legovini, Steffen Prochnow, Nicolas Repp, Hinrich Harms, Roland Winkler, and the whole \LaTeX-community for support, ideas and some great software.
% 
% \bigskip
% 
% \noindent\emph{Regarding \mLyX}: The \mLyX\ port was initially done by
% \emph{Nicholas Mariette} in March 2009 and continued by
% \emph{Ivo Pletikosi\'c} in 2011. Thank you very much for your work and the contributions to the original style.

\noindent
This project thesis in Nanotechnology is a result of countless hours in front of the computer, together with poor posture, severe hairloss,
and other common health hazards associated with such dirty, dangerous, and demanding work.
However, it is also a result of the support of many people, who have helped me during this autumn, and in the years leading up to this point.

Firstly, I would like to thank my supervisors, Professor Dag W. Breiby and Professor Basab Chattopadhyay, for their guidance and support throughout the project.
You came up with a great idea for a project thesis, and my interest in the topic has remained high since the beginning.

It has also been pleasant to get support from Dr. Fredrik Mürer, who demonstrated a tremendous interest in the project, and came with wise advice and suggestions.

There is, however, another person who has ensured that I possessed the necessary skills and structured methodology to complete this project.
During my time working at CrayoNano AS, Dr. Magnus Moreau was a great mentor, and working together with him on our simulation project prepared me for the challenges I have faced this autumn.
Without that experience, I do not believe I would have had the luxury of being properly satisfied with the results I have obtained in this limited amount of time.

I would also like to thank my friends and family. I am now ready for a social life again; at least for some weeks.
If you are reading this because I have proudly handed you my thesis, and you feel the pressure to read it to be polite,
the TLDR version would be to enjoy the aesthetic figures and then skipping to Chapter \ref{ch:optimisation_performance}.
Thank you for your patience.

Abschließend möchte ich der Technische Universität München "Servus!" und "Prost!" sagen.
Viele von den Themen, die in dieser Arbeit relevant waren, habe ich während meiner Zeit an der TUM gelernt.
%Obwohl ich nur ein Jahr an der TUM studiert habe, war sie eine sehr wichtige Zeit,    



\noindent\textit{\myLocation, \myTime}

\smallskip

\begin{flushright}
    \begin{tabular}{m{5cm}}
        \\ \hline
        \centering\myName \\
    \end{tabular}
\end{flushright}


\endgroup